Legion: Expressing Locality and Independence with Logical Regions

### 2012-08-10 doc/sc2012/experiments.tex
Working on some formatting

\begin{figure}
\includegraphics[scale=0.48]{figs/CircuitMem.pdf}
\caption{Tasks and data for the circuit simulation on a cluster of GPUs.}
\label{fig:gpumapping}
\end{figure}

@@

\subfigure[Overhead of circuit simulation on Keeneland with 3 GPUs/node.]
{
\includegraphics[scale=0.4]{figs/circuit_overhead.pdf}
\label{fig:ckt_overhead}
}
\vspace{-2mm}
\caption{Circuit simulation results.}
\vspace{-6mm}
\end{figure}

@@

To measure scaling beyond a single node, three different problem sizes
were run for each of the three systems (Figure~\ref{fig:fluid_multi}).
For the smallest problem (300K particles), we observe a 20\% speedup
from 1 to 2 nodes (16 threads total), but slow
down beyond that due to communication overhead---at 4 nodes there are
twice as many ghost cells as interior grid cells.  The larger problem
sizes (2.4M and 19M particles) do much better, with scaling of up to
5.4x when going from 1 node up to 16 because of a lower
communication-to-computation ratio.

@@

%\subfigure[Effect of load-balanced partitioning.]
%{
%\includegraphics[scale=0.4]{figs/fluid_balance.pdf}
%\label{fig:fluid_balance}
%}
\vspace{-2mm}
\caption{Fluid simulation results.}
\vspace{-6mm}
\end{figure}

>>>>

\begin{figure}
\includegraphics[scale=0.48]{figs/CircuitMem.pdf}
\caption{Tasks and data for the circuit simulation on a cluster of GPUs. \label{fig:gpumapping}}
\vspace{-6mm}
\end{figure}

@@

\subfigure[Overhead of circuit simulation on Keeneland with 3 GPUs/node.]
{
\includegraphics[scale=0.4]{figs/circuit_overhead.pdf}
\label{fig:ckt_overhead}
}
\vspace{-3mm}
\caption{Circuit simulation results.}
\vspace{-6mm}
\end{figure}

@@

To measure scaling beyond a single node, three different problem sizes
were run on each of the three systems.
The results are presented in Figure~\ref{fig:fluid_multi}.
For the smallest problem (300K particles), we observe a 20\% speedup
from 1 to 2 nodes (16 threads total), but slow
down beyond that due to communication overhead; at 4 nodes there are
twice as many ghost cells as interior grid cells.  The larger problem
sizes (2.4M and 19M particles) perform much better, with scaling of up to
5.4x when going from 1 node to 16 because of a lower
communication-to-computation ratio.

@@

%\subfigure[Effect of load-balanced partitioning.]
%{
%\includegraphics[scale=0.4]{figs/fluid_balance.pdf}
%\label{fig:fluid_balance}
%}
\vspace{-0mm}
\caption{Fluid simulation results.}
\vspace{2mm}
\end{figure}
